\mytitle{}

### 2019-09-23 paper/paper-revised.tex
Progress on revised paper for TNSM
Now includes results on SPIFFY, with some light discussion as to their
relevance. WIP on the rest of the changes mandated...

% !TeX document-id = {e7fef4b9-afbc-4e81-94aa-c4847183d047}
% !BIB program = biber
\documentclass[10pt, times, comsoc]{IEEEtran}
\usepackage{nopageno}

@@

@@

\usepackage{etoolbox}
\usepackage[binary-units, per-mode=symbol]{siunitx}
\robustify\bfseries
\sisetup{detect-all, range-phrase=--, range-units=single, detect-weight=true,detect-inline-weight=math}

@@

%bib
\usepackage[style=ieee,maxnames=3,mincitenames=1,maxcitenames=2,maxbibnames=99,
mincrossrefs=99,minxrefs=99,
sortcites,
%backend=bibtex,
uniquelist=false]{biblatex}
\addbibresource{papers-off.bib}
\addbibresource{confs-off.bib}
\addbibresource{books-off.bib}
\addbibresource{rfc.bib}
\addbibresource{misc.bib}

@@

%?? Discuss the most important conclusions before the outline.
We find that the existing work for this task \cite{DBLP:journals/eaai/MalialisK15} fails to account for congestion-aware traffic (i.e., TCP) and deployment environments with high host density per egress point, achieving poor results due to an overly coarse view of the network.
The approach we identify to remedy this is to make throttling decisions on a per-source basis, and we present the engineering decisions this mandates: updating RL agents from multiple traces per timestep, timed random sequential action computation and a supporting \emph{software-defined network} (SDN) architecture.
In tandem with the development and evaluation of an effective state space and model, we provide the design of a second model inspired by past work on algorithmic DDoS prevention, as an example of the integration of domain-specific knowledge.
Our introduction of per-source decisions improves substantially upon the state-of-the-art when acting upon most internet traffic (i.e., congestion-aware protocols), and we show that our second model achieves excellent performance for high host density in this case.
Crucially, both models remain protocol- and content-agnostic to offer future-proofing against the rollout of future protocols like QUIC \cite{DBLP:conf/sigcomm/LangleyRWVKZYKS17}.
%?? Also algorithmic enhancements such as multiple actions per timestep, 
%?? PROTOCOL-AGNOSTIC -- HOW WILL THESE THINGS COPE WITH QUIC ET AL.?!?!
Briefly, this paper contributes:
\begin{itemize}
%	\item A DDoS mitigation system based on direct-control reinforcement learning, designed for deployment in real-world software-defined networks (\cref{sec:environment-and-rl-algorithm,sec:acting-on-individual-sources}).
%	\item Important weaknesses and flaws in the past design and evaluation of similar techniques \cite{DBLP:journals/eaai/MalialisK15}. We offer a deconstruction and empirical study on their formulation, flaws, and risk factors concerning different traffic distributions---in addition, we demonstrate modifications enabling deployment in real-world software-defined networks (\cref{sec:performance-in-an-emulated-environment}).
	\item Two source-level granularity approaches to RL-driven DDoS prevention (\emph{Instant} and \emph{Guarded} action models), improving upon past aggregate-based models (\cref{sec:ddos-mitigation-with-per-flow-reinforcement-learning}).
	\item An in-depth investigation into suitable features for an automatic DDoS mitigation system, with qualitative and quantitative justification (\cref{sec:rethinking-the-state-space}).
	\item Reactive simulations of HTTP and VoIP web-server traffic, designed to test system characteristics that packet trace playback fails to capture (\cref{sec:a-new-normal}).
	\item An empirical evaluation of our new models against the state-of-the-art in RL-based DDoS mitigation using these new traffic models (\cref{sec:the-results-of-doing-so}), alongside a discussion of security concerns and real-world deployment (\cref{sec:discussion}).
\end{itemize}

@@

We assume that the deployment environment is a moderately complex software-defined network, because the paradigm offers features which can directly benefit RL agents acting within.
The OpenFlow protocol allows a controller (or other authorised hosts) to install complex actions, forwarding rules and logic into a switch at runtime.
Furthermore, networks of this kind more naturally enable the future use of \emph{network function virtualisation}, a technology which could allow relocation and easy installation of learners.
Agents communicate with their co-hosted OpenFlow-enabled switches---running a modified version of \emph{Open vSwitch} (OVS) \cite{open-vswitch}---to install probabilistic packet-drop rules.

@@

\begin{figure}
	\centering
	\resizebox{0.8\linewidth}{!}{
		\begin{tikzpicture}[
		texts/.style = {text=black},
		labeltexts/.style = {text=gray},
		treeline/.style = {draw=uofgburgundy},
		treenode/.style = {texts, circle, centered, fill=white, treeline},
		load/.style = {fill=uofgcobalt},
		loadline/.style = {draw=uofgcobalt, line width=0.75mm},
		loadhide/.style = {fill=uofgcobalt!40!white},
		external/.style = {fill=uofgrust},
		externalhide/.style = {fill=uofgrust!40!white},
		hideline/.style = {draw=uofgsandstone!40!white},
		hidenode/.style = {treenode, hideline},
		grow'=right
		]
		\node [treenode, loadhide, label={[texts]above:Agent 1}] (mainagent) {};
		\node [treenode, loadhide, right = of mainagent] (inner0) {};
		\node [treenode, loadhide, above right = 0.5cm and 1cm of inner0] (inner1) {};
		\node [hidenode, below right = 0.5cm and 1cm of inner0] (inner2) {};
		\node [treenode, loadhide, below right = 0.5cm and 1cm of inner1] (inner3) {};
		\node [treenode, loadhide, right = of inner3] (inner4) {};
		\node [treenode, loadhide, above right = 0.5cm and 1cm of inner4, label={[texts]above:$s_0$}] (s0) {};
		\node [hidenode, below right = 0.5cm and 1cm of inner4, label={[labeltexts]above:$s_1$}] (s1) {};

		\node [hidenode, above left = 0.5cm and 0.5cm of inner1, label={[labeltexts]above:Agent 2}] (agent2) {};
		\node [hidenode, below left = 0.5cm and 0.5cm of inner2, label={[labeltexts]below:Agent 3}] (agent3) {};

@@

\subsection{Systems Considerations}
Taking many actions per-timestep means that any agents are assigned a larger, and potentially unbounded, set of tasks to perform every time they receive load and flow statistics from the network and their parent switch.
This introduces some potential issues: the inability to respond to unexpected changes in flow state, delayed service of new flows, and risks that flow states become outdated.
At their worst, these risks present additional attack surface to an adversary.
To adapt to these problems, we make use of \emph{timed random sequential} updates.

Each agent begins with an empty work list.
For the set of flows active in any timestep, we shuffle the list and perform as many action calculations and updates as possible, within a set time limit.
Uncompleted work is passed on to the next timestep, until the list is emptied, at which point is is repopulated using the set of available measurements.
To ensure that flow control actions are made with recent information, we combine state vectors for unvisited flows in the current work set, and replace the stored vector for all others.
State vector combination is done by summing deltas and packet counts, updating means via weighted sums, and replacing all other fields with the newest measurements.
Following \citeauthor{DBLP:conf/sigcomm/ChenL0L18}'s observations concerning short flows \cite{DBLP:conf/sigcomm/ChenL0L18}, we maintain a deadline of \SI{1}{\milli\second}---in tests, an agent is typically able to process around 3 flows in this time.
We expect this should be tuned based on the frequency at which statistics arrive.

@@

\section{A New Normal}\label{sec:a-new-normal}

@@

Hosts send RTP traffic with Salsa20 encrypted payloads---audio frames of length \SI{20}{\milli\second} at a target \SI{96}{\kilo\bit\per\second}.
We generate similar traffic at hosts by replaying anonymised traces gathered in general use and tabletop RPG servers; each trace contains only the size of each audio payload, entries denoting missed packets, and the duration of silent periods.
We trim these silent periods to a maximum \SI{5}{\second} due to the lengthy talk/silence bursts introduced by users in RPG servers, and estimate the size of missed packets by taking an exponentially-weighted moving average over known sizes.
Hosts punctuate audio frames with a 4-byte keepalive every \SI{5}{\second}.
All traffic passes over a central server which groups hosts into rooms, and is forwarded to other participants; we do not replicate pre-call Websocket traffic which would be used for authentication.
There is no peer-to-peer traffic---the server acts as a TURN relay \cite{rfc5766} for all hosts.
%?? Reflective factor among \emph{authenticated hosts}.

@@

We compare our work most naturally against the MARL approach introduced by \textcite{DBLP:journals/eaai/MalialisK15}, the state-of-the-art in RL-based DDoS prevention.
We are most interested in seeing how their approach contrasts with ours across different topologies and workloads.
Different network environments will also impose different levels of host density, where popular web servers may have orders of magnitude more clients than egress points from their network---we aim to see how these characteristics affect performance and learning rate.

@@

We now examine the performance of our two new models (\emph{Instant}, \emph{Guarded}) as compared against existing RL work (\emph{Marl}) under different traffic behaviour and topologies, varying the host-to-learner ratio $n$ and environment.
%?? Probably best just to look at top level stuff, and THEN a simplified comparison for each intended improvement (like banded rewards).
%Additionally, we examine the performance effects of environmental characteristics and potential improvements: negative reinforcement, the case where one agent makes all decisions, and pre-training on individual features.
We present the average rewards for all combinations of these factors in \crefrange{tab:av-vals}{tab:av-ecmp-vals}---these provide a rough idea of expected performance, giving the highest-performing model in bold.
Average rewards take into account any portions of time that an agent allows illegal system states.
Several plots augment this, illustrating peak performance or the amount of time which an agent requires to learn.

@@

	\expandableinput ../tables/tnsm-avg-reward.tex
\end{table}
\begin{table}
	\centering
	\caption{Average reward for combinations of model, host density and traffic class with multiple destinations.\label{tab:av-ecmp-vals}}

	\expandableinput ../tables/tnsm-ecmp-avg-reward.tex
\end{table}

\subsection{Congestion-unaware traffic}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/udp-2}
%	
%	\caption{
%		Online performance for $n=2$ hosts per egress point when benign traffic is UDP-like.
%		Although Marl++ offers a marked improvement (a peak $\sim$\SI{30}{\percent} more benign traffic arrives unimpeded), SPF significantly underperforms for this relatively simple topology.
%		Non-SPF agents start off reasonably well, slowly learning better policies.
%		\label{fig:udp-2}
%	}
%\end{figure}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/udp-16}
%	
%	\caption{
%		Online performance for $n=16$ hosts per egress point when benign traffic is UDP-like.
%		Marl++ remains marginally ahead of its predecessor, though both have undergone a significant drop in effectiveness.
%		SPF, remarkably, displays performance on par with Marl++ for this more difficult topology.
%		Both of the new models take longer to train, but achieve better peak and average performance than Marl.
%		\label{fig:udp-16}
%	}
%\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{../plots/tnsm-udp-box-separate}

@@

In a single-destination network, we observe that Marl's performance degrades as $n$ increases.
Typically, our \emph{Instant} agent design achieves the best performance in multi-agent mode, reducing collateral damage above the current state-of-the-art, but sharply degrades at low $n$ when agents share experience.
We see a reversal of this trend for the \emph{Guarded} model, which improves as $n$ increases and in single-agent mode---when $n\ge4$, the single-agent variant offers consistent improvement.
%Across all choices of $n$, we see that Marl++ exhibits reduced collateral damage compared to Marl, with SPF starting poorly yet becoming more effective for larger $n$ (\cref{tab:av-vals}, \emph{Capped}, UDP).
\Cref{fig:udp-tree-box} shows the preserved traffic in multi-agent mode.

%?? Discuss multi-dest topol once all results available.
When defending multiple destinations, we see a sharp decrease in the effectiveness of all agent designs.
Our \emph{Instant} and \emph{Guarded} designs become more effective as $n$ increases, while Marl's effectiveness is roughly constant (aside from the outlier at $n=12$).

\subsection{Congestion-aware traffic}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/tcp-2}
%	
%	\caption{
%		Online performance for $n=2$ hosts per egress point when benign traffic is TCP-like.
%		Marl++ and Marl achieve very similar performance, starting off similarly well without notable improvement over an episode.
%		SPF's performance is disappointingly close to baseline, indicating that it is as useful as having no defence system.
%		\label{fig:tcp-2}
%	}
%\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{../plots/tnsm-tcp-box-single}

	\caption{
		Online performance for HTTP benign traffic in a single-destination network, single-agent mode.
		\emph{Instant} and \emph{Guarded} exhibit essentially identical efficacy at $n~=~2$, protecting less traffic than Marl.
		Only \emph{Guarded}'s performance rapidly increases with $n$, achieving considerably better median performance and lower variance than the other models.
		The longer tails of outliers typically indicate the longer training time the new models require---we observe that \emph{Guarded} typically has considerably lower variance once it has converged on a stable policy.
		\label{fig:tcp-tree-box}
	}
\end{figure}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.95\linewidth]{../plots/tnsm-tcp-box-single}
%	
%	\caption{
%		Online performance for HTTP benign traffic in a single-destination network, single-agent mode.
%		?? DO I need this?
%		\label{fig-tcp-tree-box-single}
%	}
%\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{../plots/tnsm-tcp-16-single}

@@

\Cref{tab:av-vals} shows that Marl offers a low (though fairly consistent) level of protection for TCP traffic, which the \emph{Instant} agent offers no substantial improvement over.
However, \emph{Guarded} agents offer a remarkable improvement for this class of traffic, particularly when experience can be shared---offering a \SI{2.21}{$\!\times$} improvement over the state-of-the art during training, which is made clearer in \cref{fig:tcp-tree-box}.
\Cref{fig:tcp-tree-16} shows that this model can protect a peak \SI{80}{\percent} of TCP traffic (\SI{2.5}{$\!\times$} improvement) after just \SI{100}{\second}, but also that all of the new models require considerably longer than Marl to learn their best-achieving policy.
%SPF reaches a stronger plateau before \emph{both}, remaining more consistent and appearing to continue learning.

%?? Discuss multi-dest topol once results available.
We observe that the same trends present themselves in the multi-destination topology: \emph{Guarded} remains the best fit for TCP, in both training modes.
Crucially, the rigid tree of learners and teams which define Marl, along with its lack of action granularity, seem to be a poor fit in this environment.

@@

%Finally, it is crucial to note that the models and techniques presented here are an improvement , this work still trails behind existing (exact) DDoS flow detection mechanisms.
Most importantly, what we wish to impart is the knowledge that while the models and techniques we present here are a significant improvement over past RL-based work, this work still trails behind existing (exact) DDoS flow detection mechanisms.
Although we have conducted work to map the territory to some extent, there are still more advancements to be made before RL-based DDoS defence is truly competitive.
The benefits we have at present are, however, substantial.
What we offer above the alternate approaches we discuss in \cref{sec:related-work} are potentially more flexible deployments and low-overhead decision-making, without requiring active measurement or the network resources and capabilities that the most effective techniques rely upon.
The techniques we propose offer substantial improvements for the defence of congestion-aware traffic, which remains the most prevalent class of traffic on the internet today.
Moreover, our decision making processes are entirely agnostic of the protocol or content of inbound traffic, offering future-proofing against the introduction of new transports.

>>>>

% !TeX document-id = {b3181d9a-ffe0-4331-a65c-c7fb8f275531}
% !BIB program = biber
\documentclass[10pt, times, comsoc]{IEEEtran}
\usepackage{nopageno}

@@

\usepackage[normalem]{ulem}

@@

\usepackage{etoolbox}
\usepackage[binary-units, per-mode=symbol]{siunitx}
\robustify\bfseries
\robustify\emph
\robustify\uline
\sisetup{detect-all, range-phrase=--, range-units=single, detect-weight=true,detect-inline-weight=math, table-format=1.3}

@@

%bib
\usepackage[style=ieee,minnames=1,maxcitenames=2,maxbibnames=2,
mincrossrefs=99,minxrefs=99,
sortcites,
%backend=bibtex,
uniquelist=false]{biblatex}
\addbibresource{papers-off.bib}
\addbibresource{confs-off.bib}
\addbibresource{books-off.bib}
\addbibresource{rfc.bib}
\addbibresource{misc.bib}

@@

%?? Discuss the most important conclusions before the outline.
We find that the existing work for this task \cite{DBLP:journals/eaai/MalialisK15} fails to account for congestion-aware traffic (i.e., TCP) and deployment environments with high host density per egress point, achieving poor results due to an overly coarse view of the network.
The approach we identify to remedy this is to make throttling decisions on a per-source basis, and we present the engineering decisions this mandates: updating RL agents from multiple traces per timestep, timed random sequential action computation and a supporting \emph{software-defined network} (SDN) architecture.
In tandem with the development and evaluation of an effective state space and model, we provide the design of a second model inspired by past work on algorithmic DDoS prevention, as an example of the integration of domain-specific knowledge.
Our introduction of per-source decisions improves substantially upon the state-of-the-art when acting upon most internet traffic (i.e., congestion-aware protocols), and we show that our second model achieves excellent performance for high host density in this case.
Crucially, both models remain protocol- and content-agnostic to offer future-proofing against the rollout of future protocols like QUIC \cite{DBLP:conf/sigcomm/LangleyRWVKZYKS17}.
%?? Also algorithmic enhancements such as multiple actions per timestep, 
%?? PROTOCOL-AGNOSTIC -- HOW WILL THESE THINGS COPE WITH QUIC ET AL.?!?!

\subsection{Contributions}
This paper contributes two source-level granularity approaches to RL-driven DDoS prevention (\emph{Instant} and \emph{Guarded} action models), improving upon past aggregate-based models (\cref{sec:ddos-mitigation-with-per-flow-reinforcement-learning}).
These are designed to make effective decisions irrespective of protocol, and to act on individual flows at the edge of network topologies with arbitrary shape and size.

We offer an in-depth investigation into suitable features for an automatic DDoS mitigation system, with qualitative and quantitative justification (\cref{sec:rethinking-the-state-space}).
These features have been suggested by past studies into DDoS prevention, and have been independently tested within their own contexts.
Our study is the first attempt to quantify the individual efficacy of each in an RL-focussed setting.

We implement reactive simulations of HTTP and VoIP web-server traffic, designed to test system characteristics that packet trace playback fails to capture (\cref{sec:a-new-normal}).
To our knowledge, this is the first attempt to study or replicate Opus-based VoIP traffic, which has become commonplace since the codec's release in 2012.
These new traffic models inform an empirical evaluation of our new models against the state-of-the-art in RL-based DDoS mitigation using (\cref{sec:the-results-of-doing-so}), alongside a discussion of security concerns and real-world deployment (\cref{sec:discussion}).
Observing that past work has been compared only against AIMD \cite{DBLP:journals/ton/YauLLY05}, we additionally compare our work against SPIFFY \cite{DBLP:conf/ndss/KangGS16}, reuniting two divergent strands of research and grounding the study of RL-based DDoS defences.

@@

We assume that the deployment environment is a moderately complex software-defined network, because the paradigm offers features which can directly benefit RL agents acting within.
The OpenFlow protocol allows a controller (or other authorised hosts) to install complex actions, forwarding rules and logic into a switch at runtime.
Furthermore, networks of this kind more naturally enable the future use of \emph{network function virtualisation}, a technology which could allow relocation and easy installation of learners (e.g., as examined by \textcite{TNSM-that-guys-paper}).
Agents communicate with their co-hosted OpenFlow-enabled switches---running a modified version of \emph{Open vSwitch} (OVS) \cite{open-vswitch}---to install probabilistic packet-drop rules.

@@

\begin{figure}
	\centering
	\resizebox{0.65\linewidth}{!}{
		\begin{tikzpicture}[
		texts/.style = {text=black},
		labeltexts/.style = {text=gray},
		treeline/.style = {draw=uofgburgundy},
		treenode/.style = {texts, circle, centered, fill=white, treeline},
		load/.style = {fill=uofgcobalt},
		loadline/.style = {draw=uofgcobalt, line width=0.75mm},
		loadhide/.style = {fill=uofgcobalt!40!white},
		external/.style = {fill=uofgrust},
		externalhide/.style = {fill=uofgrust!40!white},
		hideline/.style = {draw=uofgsandstone!40!white},
		hidenode/.style = {treenode, hideline},
		grow'=right
		]
		\node [treenode, loadhide, label={[texts]above:Agent 1}] (mainagent) {};
		\node [treenode, loadhide, right = of mainagent] (inner0) {};
		\node [treenode, loadhide, above right = 0.2cm and 1cm of inner0] (inner1) {};
		\node [hidenode, below right = 0.2cm and 1cm of inner0] (inner2) {};
		\node [treenode, loadhide, below right = 0.2cm and 1cm of inner1] (inner3) {};
		\node [treenode, loadhide, right = of inner3] (inner4) {};
		\node [treenode, loadhide, above right = 0.2cm and 1cm of inner4, label={[texts]above:$s_0$}] (s0) {};
		\node [hidenode, below right = 0.2cm and 1cm of inner4, label={[labeltexts]above:$s_1$}] (s1) {};

		\node [hidenode, above left = 0.2cm and 0.5cm of inner1, label={[labeltexts]above:Agent 2}] (agent2) {};
		\node [hidenode, below left = 0.2cm and 0.5cm of inner2, label={[labeltexts]below:Agent 3}] (agent3) {};

@@

\subsection{Systems Considerations}
Taking many actions per timestep means that any agents are assigned a larger, and potentially unbounded, set of tasks to perform every time they receive load and flow statistics from the network and their parent switch.
This introduces some potential issues: the inability to respond to unexpected changes in flow state, delayed service of new flows, and risks that flow states become outdated.
At their worst, these risks present additional attack surface to an adversary.
To adapt to these problems, we make use of \emph{timed random sequential} updates.

Each agent begins with an empty work list.
For the set of flows active in any timestep, we shuffle the list and perform as many action calculations and updates as possible, within a set time limit.
Uncompleted work is passed on to the next timestep, until the list is emptied, at which point it is repopulated using the set of available measurements.
To ensure that flow control actions are made with recent information, we combine state vectors for unvisited flows in the current work set, and replace the stored vector for all others.
State vector combination is done by summing deltas and packet counts, updating means via weighted sums, and replacing all other fields with the newest measurements.
Following \citeauthor{DBLP:conf/sigcomm/ChenL0L18}'s observations concerning short flows \cite{DBLP:conf/sigcomm/ChenL0L18}, we maintain a deadline of \SI{1}{\milli\second}---in tests, an agent is typically able to process around 3 flows in this time.
We expect this should be tuned based on the frequency at which statistics arrive.

@@

\section{Modelling Normal Traffic}\label{sec:a-new-normal}

@@

Hosts send RTP traffic with Salsa20 encrypted payloads---audio frames of length \SI{20}{\milli\second} at a target \SI{96}{\kilo\bit\per\second}.
We generate similar traffic at hosts by replaying anonymised traces gathered in general use and tabletop RPG servers; each trace contains only the size of each audio payload, entries denoting missed packets, and the duration of silent periods.
We trim these silent periods to a maximum \SI{5}{\second} due to the lengthy talk/silence bursts introduced by users in RPG servers, and estimate the size of missed packets by taking an exponentially-weighted moving average over known sizes.
Hosts punctuate audio frames with a 4-byte keepalive every \SI{5}{\second}.
All traffic passes over a central server which groups hosts into rooms, and is forwarded to other participants; we do not replicate pre-call Websocket traffic which would be used for authentication.
There is no peer-to-peer traffic---the server acts as a TURN relay for all hosts.
%?? Reflective factor among \emph{authenticated hosts}.

@@

We compare our work most naturally against the MARL approach introduced by \textcite{DBLP:journals/eaai/MalialisK15}, the state-of-the-art in RL-based DDoS prevention.
We are most interested in seeing how their approach contrasts with ours across different topologies and workloads.
Different network environments will also impose different levels of host density, where popular web servers may have orders of magnitude more clients than egress points from their network---we aim to see how these characteristics affect performance and learning rate.
Marl is already known to outperform the AIMD \cite{DBLP:journals/ton/YauLLY05} approach to DDoS mitigation, although the state of the art has long since moved on.

To paint a more current picture, we compare our work against an effective modern-day algorithmic approach, SPIFFY \cite{DBLP:conf/ndss/KangGS16}.
SPIFFY tests a proportion of flows by rerouting them through an alternate path with higher bandwidth, and observing how their speed has changed some time later.
We compare ourselves against this approach to position our new RL agent designs against the modern state of the art, observing that SPIFFY has a similar mode of interaction to RL-based systems (taking action, observing an effect, and acting once again) and does not rely on protocol characteristics or signatures.
We make the simplifying assumption that a suitable unused path exists (with identical bandwidth to the server's link).
We test \SI{10}{\percent} of active flows at a time (according to the authors' observation that there is a factor of \num{10} difference between the ideal and achieved bandwidth expansion factor), excluding flows below \SI{50}{\kilo\bit\per\second} and requiring a \SI{3}{$\times$} bandwidth expansion from legitimate flows, making a judgement after \SI{5}{\second}.

@@

We now examine the performance of our two new models (\emph{Instant}, \emph{Guarded}) as compared against existing RL work (\emph{Marl}) under different traffic behaviour and topologies, varying the host-to-learner ratio $n$ and environment.
%?? Probably best just to look at top level stuff, and THEN a simplified comparison for each intended improvement (like banded rewards).
%Additionally, we examine the performance effects of environmental characteristics and potential improvements: negative reinforcement, the case where one agent makes all decisions, and pre-training on individual features.
We present the average rewards for all combinations of these factors in \crefrange{tab:av-vals}{tab:av-ecmp-vals}---these provide a rough idea of expected performance, giving the highest-performing model in bold and underlining the best RL-based model.
Average rewards take into account any portions of time that an agent allows illegal system states.
Several plots augment this, illustrating peak performance or the amount of time which an agent requires to learn.

@@

	\resizebox{0.8\linewidth}{!}{
		\expandableinput ../tables/tnsm-tree-avg-reward-spiffy.tex
	}
\end{table}
\begin{table}
	\centering
	\caption{Average reward for combinations of model, host density and traffic class with multiple destinations.\label{tab:av-ecmp-vals}}

	\resizebox{0.8\linewidth}{!}{
		\expandableinput ../tables/tnsm-ecmp-avg-reward-spiffy.tex
	}
\end{table}

\subsection{Congestion-unaware traffic}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/udp-2}
%	
%	\caption{
%		Online performance for $n=2$ hosts per egress point when benign traffic is UDP-like.
%		Although Marl++ offers a marked improvement (a peak $\sim$\SI{30}{\percent} more benign traffic arrives unimpeded), SPF significantly underperforms for this relatively simple topology.
%		Non-SPF agents start off reasonably well, slowly learning better policies.
%		\label{fig:udp-2}
%	}
%\end{figure}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/udp-16}
%	
%	\caption{
%		Online performance for $n=16$ hosts per egress point when benign traffic is UDP-like.
%		Marl++ remains marginally ahead of its predecessor, though both have undergone a significant drop in effectiveness.
%		SPF, remarkably, displays performance on par with Marl++ for this more difficult topology.
%		Both of the new models take longer to train, but achieve better peak and average performance than Marl.
%		\label{fig:udp-16}
%	}
%\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{../plots/tnsm-udp-box-separate}

@@

In a single-destination network, we observe that Marl's performance degrades as $n$ increases.
Typically, our \emph{Instant} agent design achieves the best performance in multi-agent mode, reducing collateral damage above the current state-of-the-art, but sharply degrades at low $n$ when agents share experience.
We see a reversal of this trend for the \emph{Guarded} model, which improves as $n$ increases and in single-agent mode---when $n\ge4$, the single-agent variant offers consistent improvement.
%Across all choices of $n$, we see that Marl++ exhibits reduced collateral damage compared to Marl, with SPF starting poorly yet becoming more effective for larger $n$ (\cref{tab:av-vals}, \emph{Capped}, UDP).
\Cref{fig:udp-tree-box} shows the preserved traffic in multi-agent mode.
Interestingly, SPIFFY is unable to effectively protect constant bitrate legitimate traffic.

%?? Discuss multi-dest topol once all results available.
When defending multiple destinations, we see a sharp decrease in the effectiveness of all agent designs.
Our \emph{Instant} and \emph{Guarded} designs become more effective as $n$ increases, while Marl's effectiveness is roughly constant (aside from the outlier at $n=12$).
SPIFFY remains ineffective at protecting this class of traffic.

\subsection{Congestion-aware traffic}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/tcp-2}
%	
%	\caption{
%		Online performance for $n=2$ hosts per egress point when benign traffic is TCP-like.
%		Marl++ and Marl achieve very similar performance, starting off similarly well without notable improvement over an episode.
%		SPF's performance is disappointingly close to baseline, indicating that it is as useful as having no defence system.
%		\label{fig:tcp-2}
%	}
%\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{../plots/tnsm-tcp-box-single}

	\caption{
		Online performance for HTTP benign traffic in a single-destination network, single-agent mode.
		\emph{Instant} and \emph{Guarded} exhibit essentially identical efficacy at $n~=~2$, protecting less traffic than Marl.
		Only \emph{Guarded}'s performance rapidly increases with $n$, achieving considerably better median performance and lower variance than the other models.
		The longer tails of outliers typically indicate the longer training time the new models require---we observe that \emph{Guarded} typically has considerably lower variance once it has converged on a stable policy.
		\label{fig:tcp-tree-box}
	}
\end{figure}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.95\linewidth]{../plots/tnsm-tcp-box-single}
%	
%	\caption{
%		Online performance for HTTP benign traffic in a single-destination network, single-agent mode.
%		?? DO I need this?
%		\label{fig-tcp-tree-box-single}
%	}
%\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{../plots/tnsm-tcp-16-single}

@@

\Cref{tab:av-vals} shows that Marl offers a low (though fairly consistent) level of protection for TCP traffic, which the \emph{Instant} agent offers no substantial improvement over.
However, \emph{Guarded} agents offer a remarkable improvement for this class of traffic, particularly when experience can be shared---offering a \SI{2.21}{$\!\times$} improvement over the state-of-the art during training, which is made clearer in \cref{fig:tcp-tree-box}.
\Cref{fig:tcp-tree-16} shows that this model can protect a peak \SI{80}{\percent} of TCP traffic (\SI{2.5}{$\!\times$} improvement) after just \SI{100}{\second}, but also that all of the new models require considerably longer than Marl to learn their best-achieving policy.
Here, SPIFFY greatly outperforms all of the RL-based methods.
%SPF reaches a stronger plateau before \emph{both}, remaining more consistent and appearing to continue learning.

%?? Discuss multi-dest topol once results available.
We observe that the same trends present themselves in the multi-destination topology: \emph{Guarded} remains the best fit for TCP, in both training modes.
Crucially, the rigid tree of learners and teams which define Marl, along with its lack of action granularity, seem to be a poor fit in this environment.
SPIFFY continues to outperform the RL-based methods.

@@

%Finally, it is crucial to note that the models and techniques presented here are an improvement , this work still trails behind existing (exact) DDoS flow detection mechanisms.
Most importantly, what we wish to impart is the knowledge that while the models and techniques we present here are a significant improvement over past RL-based work, this strand still trails behind existing (exact) DDoS flow detection mechanisms where TCP traffic is concerned.
The ability to better protect VoIP traffic when compared against one of these approaches is a curious observation, which suggests that other (exact) protocol-agnostic approaches may carry hidden assumptions and is a promising direction for future investigation.
Although we have conducted work to map the territory to some extent, there are still more advancements to be made before RL-based DDoS defence is truly competitive.
The benefits we have at present are, however, substantial.
What we offer above many of the alternate approaches we discuss in \cref{sec:related-work} are potentially more flexible deployments and low-overhead decision-making, without requiring active measurement or the network resources and capabilities that the most effective techniques rely upon.
The techniques we propose offer substantial improvements for the defence of congestion-aware traffic, which remains the most prevalent class of traffic on the internet today.
Moreover, our decision making processes are entirely agnostic of the protocol or content of inbound traffic, offering future-proofing against the introduction of new transports.
